\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-10-01 paper2015asml.tex

\author{Arjun Menon$^{1}$, Sachin Chitta$^{1}$, Mark Moll$^{2}$, Lydia Kavraki$^{2}$% <-this % stops a space
\thanks{*This work was supported by ...}% <-this % stops a space
\thanks{$^{1}$SRI International, Menlo Park, CA
        {\tt\small arjun.menon@sri.com, sachin.chitta@sri.com}}%
\thanks{$^{2}$Rice University, Department of Computer Science, Houston, TX
        {\tt\small mmoll@rice.edu, kavraki@rice.edu}}%
}

@@

Robot motion study for industrial has been primarily influenced by the need to generate smooth jerk-free trajectories that minimize wear and tear of internal parts. In recent years, there has been more interest in the generation of motions for robots working in human environments, i.e. environments with clutter and people working next to the robots. Most attention, though, has been focused on generating {\em collision-free} motions. Examples include the use of randomized planners\cite{kuffner2000rrt}, trajectory optimization techniques\cite{Mrinal:2011}, and deterministic search-based techniques\cite{cohen2010search}. Such approaches have also been modified to account for other types of constraints, e.g. dynamic constraints or process constraints arising from the task.

@@

\begin{table}
\label{table:correlation}
\begin{tabular}

\end{tabular}
\end{table}

>>>>

\author{Arjun Menon$^{1}$, Pooja Kacker$^{2}$, Sachin Chitta$^{1}$% <-this % stops a space
\thanks{*This work was supported by ...}% <-this % stops a space
\thanks{$^{1}$SRI International, Menlo Park, CA
        {\tt\small arjun.menon@sri.com, sachin.chitta@sri.com}}%
\thanks{$^{2}$Independent Consultant,
        {\tt\small }}%
}

@@

Robot motion study for industrial has been primarily influenced by the need to generate smooth jerk-free trajectories that minimize wear and tear of internal parts. In recent years, there has been more interest in the generation of motions for robots working in human environments, i.e. environments with clutter and people working next to the robots. Most attention, though, has been focused on generating {\em collision-free} motions. Examples include the use of randomized planners~\cite{kuffner2000rrt}, trajectory optimization techniques~\cite{Mrinal:2011}, and deterministic search-based techniques~\cite{cohen2010search}. Such approaches have also been modified to account for other types of constraints, e.g. dynamic constraints or process constraints arising from the task.

@@

%\begin{table}
%\label{table:correlation}
%\begin{tabular}
%\end{tabular}
%\end{table}
